Boccaccio example: end to end truth for California Current

### 2019-05-23 FullBoccaccioTruthEx.Rmd
try splitting ages, failing

---
title: "Sardine example: end to end truth for California Current"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

surveyB_frombio_sardine <- surveyB_frombio[surveyB_frombio$species == "Pacific_sardine",]

@@

atBtxt2tidy <- atBtxt2 %>%
  select(Time:DIN) %>%
  #select(Time, FPL:DIN) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, biomass, -Time) %>%
  filter(species %in% c("Pacific_sardine"))

#all species comparison, time intervals hardcoded for 5 steps per year
compareB <-ggplot() +
  geom_line(data=surveyB_frombio_sardine, aes(x=time/5,y=atoutput, color="survey census B"), 
            alpha = 10/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 1/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

surveyN_sardine <- surveyN[surveyN$species == "Pacific_sardine",]

plotN <-ggplot() +
  geom_line(data=surveyN_sardine, aes(x=time/5,y=atoutput, color="survey census N"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Natage_sardine <- Natage[Natage$species == "Pacific_sardine",]

Natageplot <- ggplot(Natage_sardine, aes(x=agecl, y=atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        Natage_sardine$species))

@@

@@

len <- length_census_ss$natlength %>%
  filter(species == "Pacific_sardine")

@@

We found [after much testing](https://sgaichas.github.io/poseidon-dev/Atlantisom2SSworkflowtest.html) that the most reliable source for catch in biomass at present is the Atlantis output catch.txt file, loaded above. Here is sardine annual total catch:

@@

truecatchbio_sardine <- truecatchbio[truecatchbio$species == "Pacific_sardine",]

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_sardine, aes(x=time,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

This is true catch at age for sardine:

@@

catchage <- catch_numssshigh %>%
  filter(species == "Pacific_sardine")

@@

Sardine catch lengths:

@@

catchlen <- catch_length_census_ss$natlength %>%
  filter(species == "Pacific_sardine")

>>>>

---
title: "Boccaccio example: end to end truth for California Current"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

surveyB_frombio_ss <- surveyB_frombio[surveyB_frombio$species == "Bocaccio_rockfish",]

@@

atBtxt2tidy <- atBtxt2 %>%
  select(Time:DIN) %>%
  #select(Time, FPL:DIN) %>%
  rename_(.dots=with(groupslookup, setNames(as.list(as.character(Code)), Name))) %>%
  gather(species, biomass, -Time) %>%
  filter(species %in% c("Bocaccio_rockfish"))

#all species comparison, time intervals hardcoded for 5 steps per year
compareB <-ggplot() +
  geom_line(data=surveyB_frombio_ss, aes(x=time/5,y=atoutput, color="survey census B"), 
            alpha = 10/10) +
  geom_point(data=atBtxt2tidy, aes(x=Time/365,y=biomass, color="txt output true B"),
             alpha = 1/10) + 
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

surveyN_ss <- surveyN[surveyN$species == "Bocaccio_rockfish",]

plotN <-ggplot() +
  geom_line(data=surveyN_ss, aes(x=time/5,y=atoutput, color="survey census N"), 
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

Natage_ss <- Natage[Natage$species == "Bocaccio_rockfish",]

Natageplot <- ggplot(Natage_ss, aes(x=agecl, y=atoutput)) +
  geom_point() +
  theme_tufte() +
  labs(subtitle = paste(scenario.name,
                        Natage_ss$species))

@@

### Biological sampling: true ages (split age classes)

Bocaccio is one of many species in CCA with multiple true ages per age class. To get true ages for input into stock assessment, we need to separate the age classes. The atlantisom function `calc_stage2age` calls the `calc_Z` function, applying a total mortality rate to estimate the numbers at true age within an age class:

```{r testagecl}
# add YOY file to the config files
YOY <- load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

# load biolprm in some initialize file?
biol <- load_biolprm(d.name, biol.prm.file)

trueagesall_ss <- calc_stage2age(nums_data = Natage_ss,
                                 biolprm = biol, 
                                 yoy = YOY,
                                 fgs = funct.groups, 
                                 runprm = runpar)

@@

len <- length_census_ss$natlength %>%
  filter(species == "Bocaccio_rockfish")

@@

We found [after much testing](https://sgaichas.github.io/poseidon-dev/Atlantisom2SSworkflowtest.html) that the most reliable source for catch in biomass at present is the Atlantis output catch.txt file, loaded above. Here is bocaccio annual total catch:

@@

truecatchbio_ss <- truecatchbio[truecatchbio$species == "Bocaccio_rockfish",]

plotcatch <- ggplot() +
  geom_line(data=truecatchbio_ss, aes(x=time,y=atoutput, color="true catch bio"),
            alpha = 10/10) +
  theme_tufte() +
  theme(legend.position = "top") +
  labs(colour=scenario.name)

@@

This is true catch at age for bocaccio:

@@

catchage <- catch_numssshigh %>%
  filter(species == "Bocaccio_rockfish")

@@

Bocaccio catch lengths:

@@

catchlen <- catch_length_census_ss$natlength %>%
  filter(species == "Bocaccio_rockfish")
